### 2025-04-08 Manuscript/Manuscript.tex
writting

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

@@

\hypersetup{%
  pdftitle  = \documenttitle,
  pdfauthor = \AuthorName,
  pdfsubject= \degree,
  pdfcreator= \AuthorName,
}

@@

\DeclareMathOperator{\tr}{Tr}

@@

\begin{multicols}{2}[\begin{center}
\begin{abstract}
Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble. Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
\end{abstract}
\end{center}
Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
]
\section{Introduction}
\vspace{-0.5cm}
In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely. For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition. Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.

@@

\vspace{-0.5cm}
\section{Formulation of the problem}
\vspace{-0.5cm}
Let $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ be a set of $n$ states and $n$ probabilities, where $\rho_i$ dennotes the density matrix $\rho_i=\ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ dennotes the prior probability in which $\rho_i$ accours. Additionally, let $\rho_j$ be a state belonging to the ensemble be our target state, we aim to develope a proceadure to find $\rho_k\in\left\{\rho_i\right\}_{i=1}^n$ such that $\rho_j\neq\rho_k$.

The quantum mesurement is represented by a \gls{povm} set dennoted as $\left\{\Pi_j\right\}_j$ acting on quantum states' Hilbert space $\mathcal{H}$.

Hence, the formulation in a \gls{sdp} problem for the \gls{me} protocol for the miminization of the probability of excluding our target state from our hypothesis in the minimum error protocol reads,
\begin{align*}\label{EquationMinimumError}
	P_{\text{\gls{me}}}^e=\min_{\Pi_i}&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
\end{align*}

notice that both conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i\geq0$ stands for the \gls{povm} definition i.e. by demanding possible definitness and a sum equal to the identity we are demanding $\left\{\Pi_j\right\}_j$ to be a set of \gls{povm}s. Notice the $e$ upperindex stands for the \emph{error probability}.

Similarly the problem can trivially be formulated in an equivalent way in terms of the maximization of the \emph{success probability}, defined as the probabilty of a successfull exclusion form the point of view

\begin{align*}\label{EquationMinimumError}
	P_{\text{\gls{me}}}^s=\max_{\Pi_i}1-&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
\end{align*}
Since naturally, $P_{\text{\gls{me}}}^s+P_{\text{\gls{me}}}^e = 1$.

Moreover we refere an ensemble as a \emph{group generated ensemble} when it is the outcome of one or more unitary transformations $U_i$ applied onto a seed state such that $U_i$ generates a finite group. For instance if $U_i^n=\mathds{1}$ will lead up a $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%\setlength{\parindent}{0.0in}
%\setlength{\parskip}{0.05in}

@@

\hypersetup{%
  pdftitle  = \documenttitle,
  pdfauthor = \AuthorName,
  pdfsubject= \degree,
  pdfcreator= \AuthorName,
  hidelinks = true,
}

@@

\DeclareMathOperator{\tr}{Tr}
\usetikzlibrary{arrows.meta, positioning}

@@

\begin{multicols}{2}[\begin{center}
\begin{abstract}
Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble. Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
\end{abstract}
\end{center}
Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
]
\section{Introduction}
In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely. For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition. Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.

@@

\section{Formulation of the problem}

Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure-state density matrix, $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of state $\rho_i$. Let $\rho_j$ be the target state from this ensemble. Our goal is to develop a procedure to find another state $\rho_k \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_k \neq \rho_j$.

Quantum measurements are represented by a set of \glspl{povm}, denoted $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.

The goal of the minimum-error (\gls{me}) protocol is miminizing the probability of excluding the target state from our hypothesis. In an \gls{sdp} formulation the problem reads,
\begin{align*}
	P_{\text{\gls{me}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_i \rho_i),\\
	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

Note that the conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ define the \gls{povm} elements, ensuring positivity and completeness. The superscript $e$ in $P_{\text{\gls{me}}}^e$ stands for the \emph{error probability}.

Alternatively, the problem can be formulated in terms of the \emph{success probability} $P_{\text{\gls{me}}}^s$, which represents the probability of successful exclusion. This is other perspective is nothing but,

\begin{align*}
	P_{\text{\gls{me}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_i \rho_i)\right),\\
	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

Naturally, $P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1$.

In the case of the zero-error (\gls{ze}) protocol, the \gls{povm}s must additionally satisfy the unambiguity condition i.e. each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$, in other words,

\begin{equation*}
\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
\end{equation*}

An additional inconclusive outcome, denoted by a \gls{povm} element $\Pi_?$ (representing failure to exclude any state), must be introduced to ensure the completeness of the measurement,

\begin{equation*}
\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
\end{equation*}

If the measurement outcome corresponds to $\Pi_?$ (i.e., "?" is observed), the result is inconclusive. The corresponding \gls{sdp} for minimizing the error probability (i.e., the probability of an inconclusive outcome) in the \gls{ze} protocol is:

\begin{align*}
	P_{\text{\gls{ze}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_? \rho_i),\\
	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

Similarly, the corresponding success probability is:

\begin{align*}
	P_{\text{\gls{ze}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_? \rho_i)\right),\\
	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

Note that this formulation is analogous to the \gls{me} protocol, except for the constraint $\tr(\Pi_i \rho_i) = 0$, which enforces unambiguous discrimination.

Finally, we define a **group-generated ensemble** as one constructed by applying a finite group of unitary transformations to a fixed seed state. For example, let $U$ be a unitary operator such that $U^n = \mathds{1}$. Then the states of the ensemble are given by,

\begin{equation*}
\rho_i = U^i \rho (U^\dagger)^i, \quad i = 1, \dots, n,
\end{equation*}

where $\rho$ is the seed state. This forms a $\mathbb{Z}/n\mathbb{Z}$ generated ensemble.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
